### 2025-09-23 paper/sec/introduction.tex

Transparent documents thus turn static text into interactable, data-driven content able to expose the
evidential basis of scholarly claims, for which we envisage two use cases. First, when \textbf{authoring}
content for an online article, a journalist or scientific publisher may wish to link text to raw data so that
the evidence base for the textual claims can be explored directly from the article. Second, when
\textbf{reading} a document reporting on findings derived from open data (perhaps a scientific paper or
climate report), the reader may want to retroactively interpret parts of the text as queries over the
available data and gradually ``rationally reconstruct'' the relationship between claims in the paper and the
evidence base. This might be just to aid their own comprehension, or part of a formal peer review process.

@@

We leave implementing a full authoring plugin for an IDE such as VSCode or Cursor for future work.

>>>>

Transparent documents thus turn static text into interactable, data-driven content able to expose the
evidential basis of scholarly claims, for which we envisage two use cases. First, when \textbf{authoring}
content for an online article, a journalist or scientific publisher may wish to provide text which is linked
to the underlying data so that the evidence base for the textual claims can be explored directly from the
article. Second, when \textbf{reading} a document reporting on findings derived from open data (perhaps a
scientific paper or climate report), the reader may want to retroactively interpret parts of the text as
queries over the available data and gradually ``rationally reconstruct'' the relationship between claims in
the paper and the evidence base. This might be just to aid their own comprehension, or part of a formal peer
review process.

@@

We leave implementing a full Copilot-like authoring plugin for an IDE such as VSCode or Cursor for future
work.
